Generalized Bradley-Terry models

### 2025-02-20 inst/jss_hyper3_real.Rnw
Makefile
consistentification: rename strength to lambda

%  Process with:
%  
%  Rscript -e 'library("knitr") ; knit("jss_hyper3_real.Rnw")' && pdflatex jss_hyper3_real && open jss_hyper3_real.pdf
%

@@

<<defcalculate_sushi_H}>>=
make_sushi_H <- function(a, strength){
    h <- c(1, strength) # strength of support
    sushi_types <- c("ebi", "anago", "maguro", "ika", "uni", "sake", "tamago", "toro", "tekka", "kappa")
    ec <- # equivalence classes
        c(`ebi`  = 1, `anago` = 2, `maguro` = 1, `ika` = 1, `uni` = 1,
          `sake` = 1, `tamago` = 1, `toro` = 2, `tekka-maki` = 2,
          `kappa-maki` = 1)

@@

    for(i in seq_len(nrow(a))){
        H <- H + cheering3(sushi_types[a[i,]], e=ec, h=h)
    }
    return(H)
}
@

@@

<<calclikesushi, cache=TRUE>>=
f <- function(strength){
   H <- make_sushi_H(a, strength=strength)
   maxp(H,give=1)$`Log-likelihood`
}
s <- seq(from=0.4,to=4,len=5)
L <- sapply(s,f)
@

>>>>

%  Process with:
%  
%  Rscript -e 'library("knitr") ; knit("jss_hyper3_real.Rnw")' && pdflatex jss_hyper3_real && open jss_hyper3_real.pdf
%
%  (also the Makefile has an entry for this)

@@

<<defcalculate_sushi_H}>>=
make_sushi_H <- function(a, lambda){

    sushi_types <- c("ebi", "anago", "maguro", "ika", "uni", "sake", "tamago", "toro", "tekka", "kappa")
    ec <- # equivalence classes
        c(`ebi`  = 1, `anago` = 2, `maguro` = 1, `ika` = 1, `uni` = 1,
          `sake` = 1, `tamago` = 1, `toro` = 2, `tekka-maki` = 2,
          `kappa-maki` = 1)

@@

    for(i in seq_len(nrow(a))){
        H <- H + cheering3(sushi_types[a[i,]], e=ec, h=c(1, lambda))
    }
    return(H)
}
@

@@

<<calclikesushi, cache=TRUE>>=
f <- function(lambda){
   H <- make_sushi_H(a, lambda=lambda)
   maxp(H,give=1)$`Log-likelihood`
}
s <- seq(from=0.4,to=4,len=5)
L <- sapply(s,f)
@
